Standalone Tactics using OpenTheory

### 2012-02-14 paper.tex
Clarification

\begin{table}
\begin{center}
\begin{tabular}{||@{~}l@{~}||@{}l@{~}r@{~}|@{~}r@{~}l@{}||@{~}r@{~}||@{}l@{~}r@{~}|@{~}r@{~}l@{}||@{~}r@{~}||r@{~}||}
\hline
\textbf{Problem} & & \multicolumn{2}{c}{\textbf{Goal}} & & \textbf{Web} & & \multicolumn{2}{c}{\textbf{Proof}} & & \textbf{Total} & \textbf{Local} \\
\cline{2-4} \cline{7-9}
\textbf{Name} & & \textbf{Size} & \textbf{Time} & & \textbf{Time} & & \textbf{Size} & \textbf{Time} & & \textbf{Time} & \textbf{Time} \\
 & & \textbf{(b)} & \textbf{(s)} & & \textbf{(s)} & & \textbf{(b)} & \textbf{(s)} & & \textbf{(s)} & \textbf{(s)} \\
\hline
QBF${}_1$ & & 927 & 0.001 & & 1.064 & & 10,991 & 0.022 & & 1.088 & 0.002\\
QBF${}_2$ & & 1,474 & 0.001 & & 1.892 & & 79,944 & 0.139 & & 2.034 & 0.024\\
QBF${}_3$ & & 1,546 & 0.001 & & 1.821 & & 91,639 & 0.172 & & 1.996 & 0.024\\
SKICo${}_1$ & & 927 & 0.001 & & 1.212 & & 20,047 & 0.041 & & 1.255 & 0.000\\
SKICo${}_2$ & & 1,474 & 0.002 & & 1.557 & & 52,249 & 0.113 & & 1.673 & 0.001\\
SKICo${}_3$ & & 1,546 & 0.002 & & 1.716 & & 60,642 & 0.125 & & 1.844 & 0.005\\
\hline
\end{tabular}
\end{center}
\caption{Performance profiling for the test standalone tactics.}
\label{tab:performance}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{||@{~}l@{~}||@{}l@{~}r@{~}|@{~}r@{~}l@{}||@{~}r@{~}||@{}l@{~}r@{~}|@{~}r@{~}l@{}||@{~}r@{~}||r@{~}||}
\hline
\textbf{Tactic-} & & \multicolumn{2}{c}{\textbf{Goal}} & & \textbf{Web} & & \multicolumn{2}{c}{\textbf{Proof}} & & \textbf{Total} & \textbf{Local} \\
\cline{2-4} \cline{7-9}
\textbf{Problem} & & \textbf{Size} & \textbf{Time} & & \textbf{Time} & & \textbf{Size} & \textbf{Time} & & \textbf{Time} & \textbf{Time} \\
 & & \textbf{(b)} & \textbf{(s)} & & \textbf{(s)} & & \textbf{(b)} & \textbf{(s)} & & \textbf{(s)} & \textbf{(s)} \\
\hline
QBF-1 & & 927 & 0.001 & & 1.064 & & 10,991 & 0.022 & & 1.088 & 0.002\\
QBF-2 & & 1,474 & 0.001 & & 1.892 & & 79,944 & 0.139 & & 2.034 & 0.024\\
QBF-3 & & 1,546 & 0.001 & & 1.821 & & 91,639 & 0.172 & & 1.996 & 0.024\\
SKICo-1 & & 927 & 0.001 & & 1.212 & & 20,047 & 0.041 & & 1.255 & 0.000\\
SKICo-2 & & 1,474 & 0.002 & & 1.557 & & 52,249 & 0.113 & & 1.673 & 0.001\\
SKICo-3 & & 1,546 & 0.002 & & 1.716 & & 60,642 & 0.125 & & 1.844 & 0.005\\
\hline
\end{tabular}
\end{center}
\caption{Performance profiling for the test standalone tactics.}
\label{tab:performance}
\end{table}
